Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-08 schemes.tex
small agreed changes to the multicore section

The idea of the implemented algorithm is to represent each one of the
sub-block matrix operations: matrix-matrix multiplication,
matrix-triangle matrix multiplication, triangle-matrix system solving,
etc; as a base or \textit{kernel} operation that can be optimized
individually using \ac{SIMD} operations. Each kernel operation, at the
same time, can be represented as a task with inputs and outputs in memory.
If an algorithm is formulated conventionally and the data operations on the
sub-blocks are reordered, then it is possible to resolve data
dependencies with a \ac{DAG}. For the algorithm, as an example, a dependency
could be that a sub-block of the matrix in memory cannot be read unless
a previous writing operation was performed there. When the
\ac{DAG} is determined, then a scheduler assigns to the available cores the
execution of the kernel operations that have their dependencies satisfied.
The benefit of this method is that the synchronization relies only on
data dependencies and it does not require the insertion of artificial
synchronization points. Using this technique, the matrix inversion is
performed using an algorithm based on LU factorization
\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix multiplication is
performed by making the various matrix-matrix multiplications on the
sub-blocks.

>>>>

The idea of the implemented algorithm is to represent each one of the sub-block
matrix operations: matrix-matrix multiplication, matrix-triangle matrix
multiplication, triangle-matrix system solving, etc; as a base or
\textit{kernel} operation that can be optimized individually using \ac{SIMD}
operations. Each kernel operation, at the same time, can be represented as a
task with inputs and outputs in memory that can be assigned to the cores as soon
as the dependencies are satisfied. The benefit of this method is that the
synchronization relies only on data dependencies and it does not require the
insertion of artificial synchronization points. Using this technique, the matrix
inversion is performed using an algorithm based on LU factorization
\cite{Dongarra:2011:HPM:2132876.2132885}, and the matrix multiplication is
performed by making the various matrix-matrix multiplications on the sub-blocks.
